On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-09-13 Manuscript/manuscript.tex
Added final paragraph, edited small stuff throughout

%\of{Should I report table~\ref{tab:EffectComparison}}
%\begin{table}
%  \centering
%  \caption{Compares the various effect models by dataset, all probabilities are
%  for observing a reaction time less than 0.1 seconds. In general the model with
%  the highest probability (least extreme reaction time) is the Year Effect model.}
%  \begin{tabular}{c c c c} 
%   \toprule
%   Data Set & Year Effect & Batch Effect & Both Effects \\ 
%   \midrule
%   Old Pooled & $5.73\cdot10^{-3}$ & $5.21\cdot10^{-3}$ & $4.15\cdot10^{-3}$ \\ 
%   All Pooled & $6.84\cdot10^{-3}$ & $6.64\cdot10^{-3}$ & $5.15\cdot10^{-3}$ \\
%   \bottomrule
%  \end{tabular}
%  \label{tab:EffectComparison}
%\end{table}

@@

This paper has shown that a reaction time of 0.1 seconds is not as extreme as
one may think, and that based on the probabilities in table~\ref{tab:Sim_time},
World Athletics should consider changing the disqualification barrier to 0.8
seconds.  If they were to do so, they would allow athletes like Allen to be able
to react faster without fear of being disqualified.  The second part of this
paper showed that athletes' reaction times at the 2022 World Track and Field
Championships were generally faster than their reaction times at other
competitions.

>>>>

@@

This paper has shown that a reaction time of 0.1 seconds is not as extreme as
one may think, and that based on the probabilities in table~\ref{tab:Sim_time},
World Athletics should consider changing the disqualification barrier to 0.8
seconds.  If they were to do so, they would allow athletes like Allen to be able
to react faster without fear of being disqualified.  The second part of this
paper showed that athletes' reaction times at the 2022 World Track and Field
Championships were generally faster than their reaction times at other
competitions. Table~\ref{tab:Clusrankresults} shows multiple significant p values
that indicate differences in average reaction times for athletes who competed at
the 2022 World Track and Field Championship and another competition.  Taken
together, the results show that 2022 was an outlier and despite being disqualified,
Allen's time was not so extreme.
